Color- and piece-blind chess

### 2019-03-09 trunk/chess/papers/blind.tex
Spycheck, not yet implemented

When evaluating the first version I found that it was producing a
fairly high number of illegal positions, which was causing us to fall
back on making random moves, which is mostly boring. The second version
reduces the rate of illegal positions due to too many or too few kings.

 - we get scores with each piece
 etc.

This version, called \verb+blind_kings+, performs consistently better
than \verb+blind_yolo+ (XXX give actual record). It had an Elo World
score of XXX.

\cite{kingme}

>>>>

When evaluating the first version I found that it was predicting a
disappointingly high number of illegal positions in practice, which
was causing us to fall back on making random moves, which is mostly
boring. The second version reduces the rate of illegal positions due
to too many or too few kings~\cite{kingme}.

The model predicts a score for each type of piece in each square,
and we do not have to necessarily interpret it by always taking
the highest-scoring piece. This version first finds the two squares
with the highest scores for the white king, and same for the black
king. We take two in case the same square is predicted for both.
Then this square gets one of the kings (whichever has higher score)
and the other king goes in the highest-scoring unclaimed square. The
rest of the squares just get the highest-scoring prediction as before,
but we never predict kings.

This version, called \verb+blind_kings+, performs consistently better
than \verb+blind_yolo+ (63 wins, 45 losses, 412 draws).
% XXX could run a lot more games between these two.
% as white: 31/24/207, as black 21/32/205
It had an Elo World score of XXX.

\subsection{Spy check}

Say \verb+blind_kings+ is playing as black; it remains easy to fool it
by moving black pieces into white's camp, since they are usually then
predicted to be white pieces. We can defend against this somewhat.
Since it is illegal to capture one's own piece, there is little risk
in trying; if it is indeed our own piece then the move will be
rejected, and if it is not our piece, then capturing is good for two
reasons: One, we capture a piece, and two, we avoid having
Stockfish make a move in this incorrectly predicted board. (Of course
there are many reasons why eagerly capturing a piece can be a bad
idea, but at this level of play, an edge in material is likely worth
it.)

There is one subtlety here, which is that we can't fairly use the
information of the actual side-to-move, as above. So there is some
additional chance that we end up making a dumb move because we
both mispredicted the side-to-move and the identity of some pieces.

(XXX evaluation here)
